---
title: "Synchrony in Psychotherapy, example with F1044 patient data"
author: "Thomas Gargot"
date: "2 mars 2016"
output: 
  pdf_document: 
    toc: yes
---

```{r, echo=FALSE, eval=TRUE}
list <- list.files("CSV/csvF104422022016", full.names=TRUE)

importdata <-function(fileslist){
    data <- c()
    for (i in list){
        dataAlone <-read.csv(paste("/Users/Ofix/Documents/Fac/internat/Recherche/projets/synchro/synchroData/Git/", i, sep=""))
        data <- rbind(data, dataAlone)}
    return (data)
}
```

# Lists
## Functions list
```{r, echo=TRUE, eval=TRUE}
MeanMomentumByTime <- function(subject, indexOfvideos=1:NumberOfvideos, interval, data){
  x <- c()
  for (file in indexlist[indexOfvideos]){
        dataVector <- data[which(data$file==file), subject]
        ## with ceiling : superior limit of the round
        IntervalNumbersVideo <- ceiling(length(dataVector)/interval)
        for (i in 1:IntervalNumbersVideo){
                borneinf<- 1+(i-1)*interval
                bornesup <-i*interval
                dataVectorInterval <- dataVector[borneinf:bornesup]
                mean <- mean(dataVectorInterval, na.rm=TRUE)
                x <- c(x, mean)
        }
  }
  return (x)
}

SlidingInterval <- function(subject, indexOfvideos=1:NumberOfvideos, interval, data){
  x <- c()
  for (file in indexlist[indexOfvideos]){
      dataVector <- data[which(data$file==file), subject]
      NBofAnalysedframes <- length(dataVector)-interval+1
          for (i in 1:NBofAnalysedframes){
              borneinf<- (i)
              bornesup <-(interval-1+i)
              dataVectorInterval <- dataVector[borneinf:bornesup]
              mean <- mean(dataVectorInterval, na.rm=TRUE)
              x <- c(x, mean)
          }
  }
  return (x)
}
```

## File lists
```{r, echo=TRUE, eval=TRUE}
indexlist <- c("F1044C.VOB","F1044D1.VOB","F1044D2.VOB","F1044E.VOB","F1044F.VOB",
               "F1044G.VOB","F1044H.VOB","F1044I.VOB","F1044L.VOB","F1044M1.VOB",
               "F1044M2.VOB","F1044N.VOB", "F1044O.VOB", "F1044P.VOB", "F1044Q.VOB",
               "F1044R1.VOB","F1044R2.VOB")

labelvideolist<- c("C","D1","D2","E","F", "G","H","I","L","M1", "M2","N", "O", "P", "Q",
                   "R1","R2")

NumberOfvideos <- length(indexlist)

colOrderList <- c("blue","red", "green","orange")
```

## Participants list
```{r, echo=FALSE, eval=TRUE}
data <- importdata(list)
ParticipantsList <- names(data[,2:5])
print(ParticipantsList)
data$timeMin <- data$frame/(25*60)
```

# Presentation of the data
The timeMin is corresponding to a frame rate 25/sec.
```{r}
str(data)
summary(data)
```

# Length of the videos in minutes
```{r, echo=FALSE}
videoLengthList <-c()
for (i in indexlist){
  index<-which(data$file==i)
  videolength <- max (data$timeMin[index])
  videoLengthList <-c(videoLengthList,videolength)
}

print(videoLengthList)

par(mar=c(4,4,3,1))
barplot(videoLengthList, col="cornflowerblue", cex.axis=0.6, cex.names=0.6,
        ylab="Minutes", xlab="Video Name", las=1, names=labelvideolist, 
        main="Length in each F1044 video (min)")
        abline(h = mean(videoLengthList), lwd=2, lty=2)
        text(20,20, "Mean")
```

## Length of the videos in number of frames
```{r, echo=FALSE}
barplot(table(data$file), col="cornflowerblue", cex.axis=0.6, cex.names=0.5, cex.lab=0.8,
        main="Number of frames in each F1044 video", cex.main=0.8, ylab="Frame number", 
        names = labelvideolist, xlab="Video Name", las=1)
```

## Number of Available (True) and Not Available (False) data for each participant
```{r, echo=FALSE}
tab <- cbind(table(is.na(data[,2])),table(is.na(data[,3])),table(is.na(data[,4])), 
                                                          table(is.na(data[,5])))

par(mar=c(3,3,2,1))
barplot(tab, cex.axis = 0.7, las=2, cex.main= 1, names=ParticipantsList, 
  main="Number of available data by participant", 
  beside=TRUE, las=1, col=terrain.colors(2), ylim=c(0,600000))
legend("topright", c("T", "F"), fill=terrain.colors(2))
```

Mother and therapist are the more often present participants.

# Global Motion history
## Mean Motion history by video by participant
```{r, echo=FALSE}
meanMomentumList <-c()
meanMomentum <- function(subject){
    for (i in indexlist){
              index <- which(data$file==i)
              momentumsubject<- mean(data[index,subject], na.rm=TRUE)
              meanMomentumList <-c(meanMomentumList, momentumsubject)
    }
  return (meanMomentumList)
}

momentumfatherlist <- meanMomentum("father")
momentumMotherList <- meanMomentum("mother")
momentumTherapistList <- meanMomentum("therapist")
momentumPatientList <- meanMomentum("patient")

momentumMeanList <- rbind(momentumfatherlist, momentumMotherList, momentumPatientList, momentumTherapistList)

par(mar=c(3,3,2,1))
barplot(momentumMeanList, names=labelvideolist, las=1, cex.axis = 0.4, cex.names=0.6, 
        main="Mean Motion history in each video", beside=TRUE, 
        col=colOrderList)
par(mar=c(1,0.5,0.5,1))
legend("top", inset=.05, ParticipantsList, 
       fill=colOrderList, cex=0.7)
```

## Motion history box plots by frame (raw data), all videos
```{r, echo=FALSE}
par(mar=c(3,3,2,2))
boxplot(data$father, data$mother, data$therapist, data$patient, 
        col=colOrderList, 
        names=ParticipantsList, 
        main= "Motion history by frame box plots (raw data), all videos", las=1)
par(mar=c(1,0.5,0.5,1))
legend("topleft", ParticipantsList, fill=colOrderList, cex=0.7)
```

# Raw data and mean of Motion History on sliding and non overlapping intervals on F1044C video
## F1044C video
It is the first video of F10044C. The father, mother and therapist are present. The patient is absent.

## Raw data
```{r}
rawdatafather <- data[which(data$file=="F1044C.VOB"),]$father
rawdataMother <- data[which(data$file=="F1044C.VOB"),]$mother
rawdataTherapist <- data[which(data$file=="F1044C.VOB"),]$therapist

par(mar=c(3,3,3,2))
boxplot(rawdatafather, rawdataMother, rawdataTherapist,
        col=colOrderList[c(1,2,4)], 
        names=ParticipantsList[c(1,2,4)], 
        main= "Box plots of motion history mean 
on 11 frames non overlapping interval on F1044C video", las=1)
par(mar=c(1,0.5,0.5,1))
legend("topleft", ParticipantsList[c(1,2,4)], fill=colOrderList, cex=0.7)

summary(rawdatafather)
summary(rawdataMother)
summary(rawdataTherapist)
```

## Sliding interval
```{r}
slidedfather <- SlidingInterval("father", 1 , 11, data)
slidedmother <- SlidingInterval("mother", 1 , 11, data)
slidedtherapist <- SlidingInterval("therapist", 1 , 11, data)
slidedpatient <- SlidingInterval("patient", 1 , 11, data)

par(mar=c(3,3,2,2))
boxplot(slidedfather, slidedmother, slidedtherapist,
        col=colOrderList[c(1,2,4)], 
        names=ParticipantsList[c(1,2,4)], 
        main= "Box plot of motion history sliding interval on F1044C video", las=1)
par(mar=c(1,0.5,0.5,1))
legend("topleft", ParticipantsList[c(1,2,4)], fill=colOrderList, cex=0.7)

summary(slidedfather)
summary(slidedmother)
summary(slidedtherapist)
```

## Non overlapping interval
```{r}
fatherEleven<- MeanMomentumByTime("father", indexOfvideos=1, interval=11, data)

motherEleven <- MeanMomentumByTime("mother", indexOfvideos=1, interval=11, data)

therapistEleven <- MeanMomentumByTime("therapist", indexOfvideos=1, interval=11, data)

par(mar=c(3,3,3,2))
boxplot(fatherEleven, motherEleven, therapistEleven,
        col=colOrderList[c(1,2,4)], 
        names=ParticipantsList[c(1,2,4)], 
        main= "Box plots of motion history mean 
on 11 frames non overlapping interval for F1044C video", las=1)
par(mar=c(1,0.5,0.5,1))
legend("topleft", ParticipantsList[c(1,2,4)], fill=colOrderList[c(1,2,4)], cex=0.7)

summary(fatherEleven)
summary(motherEleven)
summary(therapistEleven)
```

# Focus on the motion history of the first 20 seconds of the first video(C) 
## Sliding interval function on a 11 frames interval
```{r}
par(mar=c(4,4,4,2))
plot(1:250, data$father[6:255], main="Mean motion history (Sliding 11 frames interval) 
     for father on F1044C video, 10 seconds ", xlab="Frame index (25/s)", ylab="Momentum",
     col="blue", type="l", lty=2, lwd=0.5)
lines(slidedfather[1:250],  col="blue", lty=1)
lines(data$mother[6:255],  col="red", lty=2, lwd=0.5)
lines(slidedmother[1:250],  col="red", lty=1)
lines(data$therapist[6:255],  col="orange", lty=2, lwd=0.5)
lines(slidedtherapist[1:250],  col="orange", lty=1)
legend("topleft", c("Raw data", "Mean on sliding Interval") , lty=c(2, 1), cex=0.7)
legend("topright", ParticipantsList[c(1,2,4)], fill=colOrderList[c(1,2,4)], cex=0.7)
```

### Non overlapping interval function on a 11 frames interval
```{r}
plot (1:24, fatherEleven[1:24], type="l", col="blue", main="Mean Momentum (non overlapping 11 frames
      intervals) for father on F1044C video, first 10 seconds", ylab="Momentum", xlab="Frame index (each 11 frames)" )
lines(motherEleven[1:24], col="red", lty=1)
lines(therapistEleven[1:24], col="green", lty=1)
legend("topleft", "Mean on non overlapping Interval" , lty=1, cex=0.7)
legend("topright", ParticipantsList[c(1,2,4)], fill=colOrderList, cex=0.7)
```

## Motion history of the father during 10-20 seconds of the first video(C) 
### Non overlapping interval function on a 11 frames interval
```{r}
par(mar=c(4,4,4,2))
plot(1:250, data$father[256:505], main="Mean motion history (Sliding 11 frames
     interval) for father on F1044C video, 10-20 seconds", xlab="Frame index (25/s)", ylab="Momentum", col="blue", type="l", lty=2, lwd=0.5)
lines(slidedfather[251:500],  col="blue", lty=1)
lines(data$mother[256:505],  col="red", lty=2, lwd=0.5)
lines(slidedmother[251:500],  col="red", lty=1)
lines(data$therapist[256:505],  col="orange", lty=2, lwd=0.5)
lines(slidedtherapist[251:500],  col="orange", lty=1)
legend("topleft", c("Raw data", "Mean on sliding Interval") , lty=c(2, 1), cex=0.7)
legend("topright", ParticipantsList[c(1,2,4)], fill=colOrderList[c(1,2,4)], cex=0.7)
```

### Non overlapping interval function on a 11 frames interval
```{r}
plot (1:24, fatherEleven[23:46], type="l", col="blue", main="Mean Momentum (non overlapping 11 frames intervals) for 
father on F1044C video, between 10-20 seconds", ylab="Momentum", xlab="Frame index (each 11 frames)", ylim=c(0, 0.009))
lines(motherEleven[23:46], col="red", lty=1)
lines(therapistEleven[23:46], col="green", lty=1)
legend("top", "Mean on non overlapping Interval" , lty=1, cex=0.7)
legend("topright", ParticipantsList[c(1,2,4)], fill=colOrderList, cex=0.7)
```

# Mean Momentum by minute plots
## First video F1044C
```{r}
fatherMinuteC<- MeanMomentumByTime("father", indexOfvideos=1, interval=1500, data)

MotherMinuteC<- MeanMomentumByTime("mother", indexOfvideos=1, interval=1500, data)

TherapistMinuteC<- MeanMomentumByTime("therapist", indexOfvideos=1, interval=1500, data)

PatientMinuteC<- MeanMomentumByTime("patient", indexOfvideos=1, interval=1500, data)

par(mar=c(4,4,4,2))
plot (1:length(fatherMinuteC), fatherMinuteC, type="l", col="blue", 
main=paste("Mean Momentum (non overlaping minute intervals) 
on F1044", "C", " video" , sep=""),
ylab="Momentum", xlab="Time by Minute" )
lines(MotherMinuteC, col="red")
lines(TherapistMinuteC, col="orange")
lines(PatientMinuteC, col="green")
legend("top", inset=.05, ParticipantsList, 
       fill=colOrderList, cex=0.7)
```

## Second video F1044D1
```{r}
fatherMinuteD1<- MeanMomentumByTime("father", indexOfvideos=2, interval=1500, data)

MotherMinuteD1<- MeanMomentumByTime("mother", indexOfvideos=2, interval=1500, data)

TherapistMinuteD1<- MeanMomentumByTime("therapist", indexOfvideos=2, interval=1500, data)

PatientMinuteD1<- MeanMomentumByTime("patient", indexOfvideos=2, interval=1500, data)

par(mar=c(4,4,4,2))
plot (1:length(fatherMinuteD1), fatherMinuteD1, type="l", col="blue", 
main=paste("Mean Momentum (non overlaping minute intervals) 
on F1044", "D1", " video" , sep=""), 
ylab="Momentum", xlab="Time by Minute" )
lines(MotherMinuteD1, col="red")
lines(TherapistMinuteD1, col="orange")
lines(PatientMinuteD1, col="green")
legend("top", inset=.05, ParticipantsList, 
       fill=colOrderList, cex=0.7)
```
To do : plot motion history by minute for each video (see with Nicolas) to check videos.