---
title: "SynchronyScoresAnalysis"
author: "Thomas Gargot"
date: "22 septembre 2016"
output: pdf_document
---

# Clean environment
```{r Clean Environment}
rm(list = ls(all.names = TRUE))
```

# Session info
```{r}
sessionInfo()
```

# Preparation of the session
```{r import libraries, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# To use this script, you must install packages (install.packages()) to install these packages if you don't have them.

# Loading libraries
## For managing data frames easilly : rbinds function
library("plyr")
## For editing string
library("stringr")
## For computing AUC of syncrony plots
library("AUC")
library("reshape2")
library("lme4")
```

## Fixed variables
```{r Variables to fix}
FileExtension <- ".MTS.avi_res.csv"

# working directory
# where this report is
#setwd("./Git/Monrado/Reports/")
setwd("/Users/Ofix/Documents/Fac/internat/Recherche/projets/synchro/synchroData/Git/Monrado/Reports")

# blue will refer to father
# red will refer to mother
# green to child
colOrderList <- c("blue","red", "green")

ParticipantsList <- c("father", "mother", "child")
```

```{r cutFrames to translate for ME}
# Import data
cutFrames <- read.csv2("../Data/CSV/Cutframes.csv")
str(cutFrames)

# Change the vector in character and cut the string in two parts minutes and second for the 4 time labels ("CutBefore"  "CutMiddle1" "CutMiddle2" "CutFinal") 
cutFrames$CutBefore <- as.character(cutFrames$CutBefore)
cutFramesCB <- strsplit(cutFrames$CutBefore, split=":")

# Compute the time in minutes from time in minutes and seconds for each video for Cut Before
Cut <- c()
for (i in 1:nrow(cutFrames)){ 
  CutBeforeAlone <- (as.numeric(cutFramesCB[i][[1]][1]) + as.numeric(cutFramesCB[i][[1]][2])/60)
  Cut <- c(Cut, CutBeforeAlone)
  }
cutFrames$CutBeforeMin <- Cut

# Compute the time in minutes from time in minutes and seconds for each video for Cut CutMiddle1
Cut <- c()
cutFrames$CutMiddle1 <- as.character(cutFrames$CutMiddle1)
cutMiddleSplit <- strsplit(cutFrames$CutMiddle1, split=":")
for (i in 1:nrow(cutFrames)){ 
  CutAlone <- (as.numeric(cutMiddleSplit[i][[1]][1]) + as.numeric(cutMiddleSplit[i][[1]][2])/60)
  Cut <- c(Cut, CutAlone)
  }
cutFrames$CutMiddle1Min <- Cut

# Compute the time in minutes from time in minutes and seconds for each video for Cut CutMiddle2
Cut <- c()
cutFrames$CutMiddle2 <- as.character(cutFrames$CutMiddle2)
cutMiddleSplit <- strsplit(cutFrames$CutMiddle2, split=":")
for (i in 1:nrow(cutFrames)){ 
  CutAlone <- (as.numeric(cutMiddleSplit[i][[1]][1]) + as.numeric(cutMiddleSplit[i][[1]][2])/60)
  Cut <- c(Cut, CutAlone)
  }
cutFrames$CutMiddle2Min <- Cut

# Compute the time in minutes from time in minutes and seconds for each video for Cut CutFinal
Cut <- c()
cutFrames$CutFinal <- as.character(cutFrames$CutFinal)
cutSplit <- strsplit(cutFrames$CutFinal, split=":")
for (i in 1:nrow(cutFrames)){ 
  CutAlone <- (as.numeric(cutSplit[i][[1]][1]) + as.numeric(cutSplit[i][[1]][2])/60)
  Cut <- c(Cut, CutAlone)
  }
cutFrames$CutFinalMin <- Cut
Cut <- c()
```

### Data dictionnary of cutFrames dataframe
* **family** : code of the family
* **CutBefore** : when the experimenter leave the room and the interaction begin character string in the form min:sec
* **CutMiddle1** : when the experimenter come back to explain that the participants are asked to have a conflictual discussion, character string in the form min:sec
* **CutMiddle2** : when the experimenter leave and the conflictual discussion begin
Between is the conflictual discussion, character string in the form min:sec
* **CutFinal** : when the experimenter come back to shut down the camera, character string in the form min:sec
* **ChildSex** : Factor variable : Male of Female
* **ParentSex** : Factor variable : Male of Female
* **CutBeforeMin** : when the experimenter leave the room and the interaction begin numeric variable in minutes
* **CutMiddle1Min** : when the experimenter come back to explain that the participants are asked to have a conflictual discussion, numeric variable in minutes
* **CutMiddle2Min** : when the experimenter leave and the conflictual discussion begin
Between is the conflictual discussion, numeric variable in minutes
* **CutFinalMin** : when the experimenter come back to shut down the camera, numeric variable in minutes

# SyncPy utilisation for creating synchrony dataframe
After extracting filtered motion motion history with mean on sliding interval (overlapping interval) of 5 frames
And after puting this data on a CSV file [slideddata.csv](../Data/CSV/filtered/log)

We import this data on python Script with panda module [Call_S_Estimator.py](../Scripts/Call_S_Estimator.py)
This script will compute the synchrony between each dyad of the interaction and of the whole group
It will return a csv file for each video [SSIXXXX.csv](../Data/CSV/Synchrony/log) with XXXX the name of the video (1606, BAJE059 etc) that we can import with R with
this following function

```{r SSInoLogFilesList}
# Create a list with the file names
print("SSI Files Directory")
SSInoLogFilesList <- list.files("../Data/CSV/Synchrony/noLog/S_estimator/noShuffle", full.name=TRUE)
#SSInoLogFilesList
```

```{r SSInolog import}
# Import and merge the data
SSInoLog <- data.frame(video="Name")
for (file in SSInoLogFilesList){
  #  print(file)
    SSIalone <- read.csv(file)
  #  print(str(SSIalone))
    SSInoLog<- rbind.fill(SSInoLog, SSIalone)}
SSInoLog$video <-as.factor(SSInoLog$video)
SSInoLog <- SSInoLog[-which(SSInoLog$video=="Name"),]
SSInoLog$Interval <- NULL
SSInoLog <- rename (SSInoLog, c("video" = "family"))
SSInoLog <- rename (SSInoLog, c("X" = "SSI-interval"))
SSInoLog$SSI<-rowSums(SSInoLog[, c("SSI_fa_ch", "SSI_mo_ch")], na.rm=T)
```

# Annotating data frames noLog
```{r SSInoLog}
SSInoLog <- merge(SSInoLog, cutFrames, by.x="family", by.y="family")
SSInoLog$LabelVideo <- rep(NA, nrow(SSInoLog)) 
SSInoLog[which(SSInoLog$Time_min <= SSInoLog$CutBeforeMin),]$LabelVideo <- "Cut"

SSInoLog[which(SSInoLog$Time_min > SSInoLog$CutBeforeMin & SSInoLog$Time_min < SSInoLog$CutMiddle1Min),]$LabelVideo <- "No Conflict"

SSInoLog[which(SSInoLog$Time_min >= SSInoLog$CutMiddle1Min & SSInoLog$Time_min <= SSInoLog$CutMiddle2Min),]$LabelVideo <- "Cut"

SSInoLog[which(SSInoLog$Time_min > SSInoLog$CutMiddle2Min & SSInoLog$Time_min < SSInoLog$CutFinalMin),]$LabelVideo <- "Conflict"

SSInoLog[which(SSInoLog$Time_min >= SSInoLog$CutFinalMin),]$LabelVideo <- "Cut"
```

## Import motion history (MH)
```{r}
MH_list <- list.files("../Data/CSV/filtered/noLog/noshuffled", full.names = TRUE)

MH <- data.frame(video="Name")

for (file in MH_list){
  #  print(file)
    MHalone <- read.csv(file)
  #  print(str(SSIalone))
    MH<- rbind.fill(MH, MHalone)}
MH <- MH[-which(MH$video=="Name"),]
MH$X <- NULL
MH <- rename (MH, c("video" = "family"))
MH$slidedParent<-rowSums(MH[, c("slidedFather", "slidedMother")], na.rm=T)
```

## Annotating dataframe MH
```{r}
#View(MH)
MH <- merge(MH, cutFrames, by.x="family", by.y="family")
MH$LabelVideo <- rep(NA, nrow(MH)) 
#for 25 frmaes by second and 60 seconds by min
MH$Time_min <- MH$frame_index/(25*60)
MH[which(MH$Time_min <= MH$CutBeforeMin),]$LabelVideo <- "Cut"

MH[which(MH$Time_min > MH$CutBeforeMin & MH$Time_min < MH$CutMiddle1Min),]$LabelVideo <- "No Conflict"

MH[which(MH$Time_min >= MH$CutMiddle1Min & MH$Time_min <= MH$CutMiddle2Min),]$LabelVideo <- "Cut"

MH[which(MH$Time_min > MH$CutMiddle2Min & MH$Time_min < MH$CutFinalMin),]$LabelVideo <- "Conflict"

MH[which(MH$Time_min >= MH$CutFinalMin),]$LabelVideo <- "Cut"
```

## Description of noLogSSI data frame
```{r SSInologdf  description , cache=FALSE}
str(SSInoLog)
#View(SSInoLog)
```

### Data dictionnary of SSInolog data frame
* **family** : code of the family
* **SSI-interval** : interval of SSI
* **Time_min** : Time in minutes
* **SSI_fa_ch** : SSI index of Synchrony between father and child
* **SSI_mo_ch** : SSI index of Synchrony between mother and child
* **SSI** : SSI index of the interaction (father-child or mother-child)
* **CutBefore** : when the experimenter leave the room and the interaction begin character string in the form min:sec
* **CutMiddle1** : when the experimenter come back to explain that the participants are asked to have a conflictual discussion, character string in the form min:sec
* **CutMiddle2** : when the experimenter leave and the conflictual discussion begin
Between is the conflictual discussion, character string in the form min:sec
* **CutFinal** : when the experimenter come back to shut down the camera, character string in the form min:sec
* **ChildSex** : Factor variable : Male of Female
* **ParentSex** : Factor variable : Male of Female
* **CutBeforeMin** : when the experimenter leave the room and the interaction begin numeric variable in minutes
* **CutMiddle1Min** : when the experimenter come back to explain that the participants are asked to have a conflictual discussion, numeric variable in minutes
* **CutMiddle2Min** : when the experimenter leave and the conflictual discussion begin
Between is the conflictual discussion, numeric variable in minutes
* **CutFinalMin** : when the experimenter come back to shut down the camera, numeric variable in minutes
* **LabelVideo** : label of the video if it is related to No Conflict period or Conflict Period 

## Description of MH data frame
```{r MH  description , cache=FALSE}
str(MH)
#View(SSInoLog)
```

### Data dictionnary of SSInolog data frame
* **family** : code of the family
* **SlidedFather** : Filtered motion History of the father
* **Time_min** : Time in minutes
* **SlidedMother* : Filtered Motion History of the mother
* **SlidedChild** :  Filtered Motion History of the child
* **SlidedParent* : Filtered Motion History of the parent (either mother or father)
* **frame index* : index of the frame (from 1st to last frame of each video)
* **CutBefore** : when the experimenter leave the room and the interaction begin character string in the form min:sec
* **CutMiddle1** : when the experimenter come back to explain that the participants are asked to have a conflictual discussion, character string in the form min:sec
* **CutMiddle2** : when the experimenter leave and the conflictual discussion begin
Between is the conflictual discussion, character string in the form min:sec
* **CutFinal** : when the experimenter come back to shut down the camera, character string in the form min:sec
* **ChildSex** : Factor variable : Male of Female
* **ParentSex** : Factor variable : Male of Female
* **CutBeforeMin** : when the experimenter leave the room and the interaction begin numeric variable in minutes
* **CutMiddle1Min** : when the experimenter come back to explain that the participants are asked to have a conflictual discussion, numeric variable in minutes
* **CutMiddle2Min** : when the experimenter leave and the conflictual discussion begin
Between is the conflictual discussion, numeric variable in minutes
* **CutFinalMin** : when the experimenter come back to shut down the camera, numeric variable in minutes
* **LabelVideo** : label of the video if it is related to No Conflict period or Conflict Period 

# Motion history score for each dyad
```{r}
par(mar=c(4,4,4,3))
for (i in unique(MH$family)){
  
    a <- paste(as.character(i), ".png", sep="")
     print(a)
     #dev.copy(file=a,device=png, bg="white",  width=640, height=352) 
   png(filename = a, width = 800, height = 600, units = "px")
        plot(MH[which(MH$family==i),]$Time_min, (MH[which(MH$family==i),]$slidedParent), 
             ylim=c(0, 0.04), col="cornflowerblue",
             main=paste("Motion History scores in", i, "family"), 
             xlab = "Time (minute)", ylab="Motion History score", 
                     lwd=2, type="l", cex.axis=0.7, xaxp=c(0,length(MH[which(MH$family==i),]$Time_min), length(MH[which(MH$family==i),]$Time_min)))
        lines(MH[which(MH$family==i),]$Time_min, MH[which(MH$family==i),]$slidedChild, col="green")
        abline(v= MH[which(MH$family==i),]$CutBeforeMin, col="green", lty=2, lwd=3)
        abline(v= MH[which(MH$family==i),]$CutMiddle1Min, col="green", lty=2, lwd=3)
       abline(v= MH[which(MH$family==i),]$CutMiddle2Min, col="red", lty=2, lwd=3)
        abline(v= MH[which(MH$family==i),]$CutFinalMin, col="red", lty=2, lwd=3)
        legend("topright", c("No conflict", "Conflict"), lty=c(2,2), lwd=c(3,3), col=c("green", "red"))

     dev.off()
   # graphics.off()
}
```

# Synchrony scores noLog for each dyad
```{r Synchrony scores noLog for each dyad, fig.width=8, fig.height=5}

par(mar=c(4,5,4,3), mfrow=c(1,1))
for (i in unique(SSInoLog$family)){
        plot(SSInoLog[which(SSInoLog$family==i),]$Time_min,
             SSInoLog[which(SSInoLog$family==i),]$SSI, 
             ylim=c(0, 0.3), 
             main=paste("Synchrony scores in", i, "family"), 
             xlab = "Time (minutes)", ylab="Synchrony score", 
             lwd=2, type="l", cex.axis=2, cex.lab=2, xaxp=c(0,length(SSInoLog[which(SSInoLog$family==i),]$Time_min), length(SSInoLog[which(SSInoLog$family==i),]$Time_min)))
#abline(v= SSInoLog[which(SSInoLog$family==i),]$CutBeforeMin, col="green", lty=2, lwd=3)
abline(v= SSInoLog[which(SSInoLog$family==i),]$CutMiddle1Min, col="orange", lty=2, lwd=5)
#abline(v= SSInoLog[which(SSInoLog$family==i),]$CutMiddle2Min
#       , col="red", lty=2, lwd=3)
#abline(v= SSInoLog[which(SSInoLog$family==i),]$CutFinalMin, col="red", lty=2, lwd=3)
#legend("topright", c("No conflict", "Conflict"), lty=c(2,2), lwd=c(3,3), col=c("green", "red"))
#max(SSInoLog[which(SSInoLog$family==i),]$SSI)), col="green")

  }
    
#SSInoLog$SSI <- as.ts(SSInoLog$SSI)

#for (i in unique(SSInoLog$family)[5:35]){
#  print(i)
#  SSI.decompose <- #decompose(SSInoLog[(which(SSInoLog$family==i)),]$SSI, type="mult")
#}
```

```{r}
ncSSI <- c()
cSSI <- c()

for (i in unique(SSInoLog$family)){
#  print (i)
  nc <- mean(SSInoLog[which(SSInoLog$LabelVideo=="No Conflict" & SSInoLog$family==i),]$SSI)
 # print(nc)
  ncSSI <- c(ncSSI, nc)
  co <-mean(SSInoLog[which(SSInoLog$LabelVideo=="Conflict"  & SSInoLog$family==i),]$SSI)
 # print (co)
  cSSI <- c(cSSI, co)
}

hist(ncSSI)
hist(cSSI)

sd(ncSSI)/sd(cSSI)

SSImean <- data.frame(sort(ncSSI, decreasing = TRUE), sort(cSSI, decreasing = TRUE))
par(mar=c(3,5,3,3))

boxplot(SSImean, names= c("No conflict", "Conflict"), ylab="Synchrony score")

#efectifs <30 donc pas de t-test
#t.test(ncSSI, cSSI, alternative = c("two.sided"),
#paired=TRUE, conf.level = 0.95)

wilcox.test(ncSSI, cSSI)
```
There isn't any difference between the mean SSI before and after the conflict.

```{r}
SSI <- SSInoLog[-which(SSInoLog$LabelVideo=="Cut"),]
names(SSI)
SSIagg <- subset(SSI, select=c(family, SSI, LabelVideo))
#View(SSIagg)
names(SSIagg)
str(SSIagg)
SSIagg$LabelVideo <- as.factor(SSIagg$LabelVideo)
names(SSIagg)
SSIagg <-aggregate(SSIagg, by=list(SSIagg$family, SSIagg$LabelVideo), FUN=mean)
#View(SSIagg)
SSIagg$family <-NULL
SSIagg$LabelVideo <-NULL
names(SSIagg) <-c("family","LabelVideo", "SSI")
par(mar= c(5,5,2,2))
plot(SSIagg[which(SSIagg$LabelVideo=="Conflict"),]$SSI,SSIagg[which(SSIagg$LabelVideo=="No Conflict"),]$SSI, xlab="Conflict SSI", ylab="No conflict SSI")
model <- lm(SSIagg[which(SSIagg$LabelVideo=="No Conflict"),]$SSI ~ SSIagg[which(SSIagg$LabelVideo=="Conflict"),]$SSI )
abline(model)
cor.test(SSIagg[which(SSIagg$LabelVideo=="Conflict"),]$SSI,SSIagg[which(SSIagg$LabelVideo=="No Conflict"),]$SSI)


#View(SSIagg)
```

There is a correlation between the synchrony before and after the conflict. 

```{r}
psycho<-read.csv2("/Users/Ofix/Documents/Fac/internat/Recherche/projets/synchro/synchroData/Monrado/Data/CSV/PsychomotData.csv")
#View(psycho)
psycho <- subset(psycho, select=c(Num._ident_videos, attachement_cluster, insecurite_level, TAS_total, global_score, STAIYB_total, BDI_total))
#View(psycho)

par(mar=c(4,4,2,1))
plot(psycho$STAIYB_total, psycho$BDI_total, main="BDI en fonction de la STAIY", xlab="STAIY", ylab="BDI")
model <- lm(psycho$BDI_total~psycho$STAIYB_total)
abline(model, lwd=2)
cor.test(psycho$BDI_total,psycho$STAIYB_total)

table(psycho$attachement_cluster)
barplot(sort(table(psycho$attachement_cluster), decreasing=TRUE), col="cornflower blue", main="Effectifs par style d'attachement")
#View(SSInoLog)
SSI <- SSInoLog[-which(SSInoLog$LabelVideo=="Cut"),]
SSIagg <- subset(SSI, select=c(family, SSI, LabelVideo))
#View(SSIagg)

str(SSIagg)
SSIagg$LabelVideo <- as.factor(SSIagg$LabelVideo)

SSIagg <-aggregate(SSIagg, by=list(SSIagg$family), FUN=mean)
#View(SSIagg)
SSIagg$family <-NULL
SSIagg$LabelVideo <-NULL
names(SSIagg) <-c("family", "SSI")
SSI <- merge(SSIagg, psycho, by.x= "family", by.y= "Num._ident_videos")

#View(SSI)
SSI$attachement_duo <- rep(NA)
SSI[which(SSI$attachement_cluster=="Secure"),]$attachement_duo <- "Secure"
SSI[which(SSI$attachement_cluster!="Secure"),]$attachement_duo <- "Unsecure"

boxplot(SSI ~ attachement_cluster, data = SSI, cex.axis=0.7, ylab="Synchrony score")
boxplot(SSI ~ attachement_duo, data = SSI, ylab="SSI")
hist(SSI[which(SSI$attachement_duo!="Secure"),]$SSI)
sd(SSI[which(SSI$attachement_duo!="Secure"),]$SSI)
hist(SSI[which(SSI$attachement_duo=="Secure"),]$SSI)
sd(SSI[which(SSI$attachement_duo=="Secure"),]$SSI)
table(SSI$attachement_duo)

barplot(table(SSI$attachement_duo), ylim=c(0,20), col="cornflowerblue")

#Effectifs inf à 30 donc pas possibles
#t.test(SSI[which(SSI$attachement_duo=="Unsecure"),]$SSI, SSI[which(SSI$attachement_duo=="Secure"),]$SSI)

wilcox.test(SSI[which(SSI$attachement_duo=="Unsecure"),]$SSI, SSI[which(SSI$attachement_duo=="Secure"),]$SSI)

SSIattach <- data.frame(c(sort(SSI[which(SSI$attachement_cluster=="FE"),]$SSI, decreasing = TRUE), rep(mean(SSI[which(SSI$attachement_cluster=="FE"),]$SSI), 2)), sort(SSI[which(SSI$attachement_cluster=="Secure"),]$SSI, decreasing = TRUE))

#View(SSIattach)
par(mar=c(3,5,3,3))

FE <- c(sort(SSI[which(SSI$attachement_cluster=="FE"),]$SSI, decreasing = TRUE), rep(mean(SSI[which(SSI$attachement_cluster=="FE"),]$SSI), 2))

boxplot(SSI[which(SSI$attachement_cluster=="Secure"),]$SSI, SSI[which(SSI$attachement_cluster=="FE"),]$SSI, names=c("Secure", "FE"), ylab="Synchrony")

t.test(SSI[which(SSI$attachement_cluster=="Secure"),]$SSI, SSI[which(SSI$attachement_cluster=="FE"),]$SSI, alternative = c("two.sided"),paired=FALSE, conf.level = 0.95)
```

```{r}
SSIM <- aggregate(SSI, by=list(SSI$family), FUN=mean)

plot(SSIM$SSI, SSIM$TAS_total)
model <- lm(SSIM$TAS_total~SSIM$SSI)
abline(model)
cor.test(SSIM$SSI, SSIM$TAS_total)

plot(SSIM$SSI, SSIM$STAIYB_total)
model <- lm(SSIM$STAIYB_total~SSIM$SSI)
abline(model)
cor.test(SSIM$SSI, SSIM$STAIYB_total)

plot(SSIM$SSI, SSIM$BDI_total)
model <- lm(SSIM$BDI_total~SSIM$SSI)
abline(model)
cor.test(SSIM$SSI, SSIM$BDI_total)
```

```{r}
#View(SSInoLog)
SSI <- SSInoLog[-which(SSInoLog$LabelVideo=="Cut"),]
SSIagg <- subset(SSI, select=c(family, SSI, LabelVideo))
#View(SSIagg)
names(SSIagg)
str(SSIagg)
SSIagg$LabelVideo <- as.factor(SSIagg$LabelVideo)
names(SSIagg)
SSIagg <-aggregate(SSIagg, by=list(SSIagg$family, SSIagg$LabelVideo), FUN=mean)
#View(SSIagg)
SSIagg$family <-NULL
SSIagg$LabelVideo <-NULL
names(SSIagg) <-c("family", "LabelVideo", "SSI")
SSI <- merge(SSIagg, psycho, by.x= "family", by.y= "Num._ident_videos")
#View(SSI)
SSI$diff <-rep(NA)
for (i in unique(SSI$family)){
SSI[which(SSI$family==i),]$diff <- 
    a <-
SSI[which(SSI$family==i & SSI$LabelVideo=="Conflict"),]$SSI - SSI[which(SSI$family==i & SSI$LabelVideo=="No Conflict"),]$SSI
  print (a)
}

SSIdiff <- data.frame(sort(c(SSI[which(SSI$attachement_cluster=="FE"),]$diff, rep(mean(SSI[which(SSI$attachement_cluster=="FE"),]$diff), 4)), decreasing = TRUE), sort(SSI[which(SSI$attachement_cluster=="Secure"),]$diff, decreasing = TRUE))
par(mar=c(3,5,3,3))
barplot(as.matrix(SSIdiff), col=terrain.colors(34), ylab="Synchrony scores", main="Sum of mean synchrony scores for all videos", names.arg = c("FE", "Secure"))
FE <- c(sort(SSI[which(SSI$attachement_cluster=="FE"),]$SSI, decreasing = TRUE), rep(mean(SSI[which(SSI$attachement_cluster=="FE"),]$SSI), 2))

t.test(SSI[which(SSI$attachement_cluster=="Secure" & SSI$LabelVideo=="Conflict"),]$diff, SSI[which(SSI$attachement_cluster=="FE"& SSI$LabelVideo=="Conflict"),]$diff, alternative = c("two.sided"),paired=FALSE, conf.level = 0.95)

boxplot(SSI[which(SSI$attachement_cluster=="Secure" & SSI$LabelVideo=="Conflict"),]$diff, SSI[which(SSI$attachement_cluster=="FE"& SSI$LabelVideo=="Conflict"),]$diff, names=c("Secure", "FE"), ylab=("Synchrony difference before and after conflict"))
```

```{r}
#View(SSI)
plot(SSI$diff, SSI$TAS_total)
model <- lm(SSI$TAS_total~SSI$diff)
abline(model)
cor.test(SSI[which(SSI$LabelVideo=="Conflict"),]$diff, SSI[which(SSI$LabelVideo=="Conflict"),]$TAS_total)
```

```{r}
table(SSI$insecurite_level)
```

```{r}
#Quantite de mvt et BDI
str(MH)
str(psycho)
MH1 <- merge(MH, psycho, by.x="family", by.y="Num._ident_videos")
MH1 <- MH1[-which(MH1$LabelVideo=="Cut"),]
str(MH1)
MHagg <- aggregate(MH1, by=list(MH1$family, MH1$LabelVideo), FUN=mean)
#View(MHagg)

```

```{r}
plot(MHagg$slidedChild, MHagg$BDI_total)
lm <- lm(MHagg$BDI_total~MHagg$slidedChild)
abline(lm)
cor.test(MHagg$slidedChild,MHagg$BDI_total)
#View(MH1)
plot(MHagg$slidedChild, MHagg$STAIYB_total)
lm <- lm(MHagg$STAIYB_total~MHagg$slidedChild)
abline(lm)
cor.test(MHagg$slidedChild,MHagg$STAIYB_total)
```


```{r}
library(reshape2)
SSIPsycho <- merge(SSInoLog, psycho, by.x="family", by.y="Num._ident_videos")
data_long <- melt(SSInoLog, id.vars = c('family', 'ChildSex', "ParentSex"),  measure.vars = c(1,2,3,4))
SSIPsycho$CutBefore <-NULL
SSIPsycho$SSI_fa_ch <-NULL
SSIPsycho$SSI_mo_ch <-NULL
SSIPsycho$CutMiddle1 <-NULL
SSIPsycho$CutMiddle2 <-NULL
SSIPsycho$CutFinal <-NULL
SSIPsycho$CutBeforeMin <-NULL
SSIPsycho$CutMiddle1Min <-NULL
SSIPsycho$CutMiddle2Min <-NULL
SSIPsycho$CutFinalMin <-NULL
SSIPsycho$global_score <-NULL
SSIPsycho <- SSIPsycho[-which(SSIPsycho$LabelVideo=="Cut"),]
#View(data_long)
write.csv(SSIPsycho, file="SSIPsycho.csv")

SSIPsycho$LabelVideo <- as.factor(SSIPsycho$LabelVideo)

mod1 <- glmer(LabelVideo ~ SSI + (1|family), data=SSIPsycho, family=binomial, nAGQ=20)
summary(mod1)
mod <- glmer(LabelVideo ~ SSI + (1|family) + ChildSex + ParentSex +  attachement_cluster, data=SSIPsycho, family=binomial, nAGQ=20)
summary(mod)


mod <- glmer(attachement_cluster ~ SSI + (1|family) + LabelVideo, data=SSIPsycho, family=binomial , nAGQ=20)
summary(mod)

mod <- glmer(attachement_cluster ~ SSI + (1|family) + LabelVideo, data=SSIPsycho, family=binomial , nAGQ=20)
summary(mod)

mod <- glmer(attachement_cluster ~ SSI + (1|family) + LabelVideo, data=SSIPsycho, family=binomial , nAGQ=20)
summary(mod)

SSIPsycho$attachement_duo <- rep(NA)
SSIPsycho[which(SSIPsycho$attachement_cluster=="Secure"),]$attachement_duo <- "Secure"
SSIPsycho[which(SSIPsycho$attachement_cluster!="Secure"),]$attachement_duo <- "Unsecure"
SSIPsycho$attachement_duo <- as.factor(SSIPsycho$attachement_duo)

mod <- glmer(attachement_duo ~ SSI + (1|family) + LabelVideo, data=SSIPsycho, family=binomial , nAGQ=20)
summary(mod)

mod1 <- glmer(LabelVideo ~ SSI + (1|family) + attachement_duo, data=SSIPsycho, family=binomial, nAGQ=20)
summary(mod1)

```



